### 2023-09-08 main.tex
jkl
lkjlkj

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
To prove this statement we introduce the following notation. We identify each state by 

@@

We first write some relations that will be useful in the proof.

@@

\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
	D_{i,j}^{2L}|\tau_{1},\ldots,\tau_{L}\rangle=-2|\tau_{1}^{'}\ldots,\tau_{L}^{'}\rangle \qquad \text{where}\qquad \tau^{'}_{x}=\begin{cases}
		\tau_{x}\quad &\text{if}\quad \tau_{x}\neq i\\
		j\quad &\text{if}\quad \tau_{x}=i
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	-2B_{i}|\Psi_{0}^{0}\rangle
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0\qquad \forall k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle \qquad \forall i\in \{1,\ldots,N-1\}
Indeed,
D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
Therefore, $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$. Indeed,
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
		\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
		(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
since 
\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0\qquad e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j\in\{1,\ldots,N-1\}$

@@

Indeed, consider \eqref{ExQ0B-charges} then we can write 

@@

	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle

@@

For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 

@@

@@

Therefore, we find 

>>>>

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

\begin{equation}\label{SteadyState-W-Good}
To prove \eqref{SteadyState-W-Good} we do some steps. 
\paragraph{Useful relations}
We introduce the following notation:

@@

We first write some relations that will be useful in the proof:
	\item For all $i\in\{1,\ldots,N-1\}$

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{i}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Dii-ref}:}
\begin{align}
	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

\paragraph{Two indices formula}
Using \eqref{BActionVoid} and \eqref{Commutativity-Gained} we have that for all $i,j\in\{1,\ldots,N-1\}$

@@

\textbf{Proof of \eqref{Two-Relation}:}
consider \eqref{ExQ0B-charges} then we can write 

@@

	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\\&
	B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber\\=&\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle

@@

\paragraph{Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 

@@

\textbf{Proof of \eqref{k-times-QB}}

@@

\paragraph{Final formula.} Therefore, we find 
